Project 1 for Complex Adaptive Systems

### 2018-02-19 paper.tex
Add figure 1 and started references section

Define the population size relative to the carrying capacity as  $x_t = n_t / k$ and define $R = birthrate - deathrate$.  Then we  get the following equation for $x_t$: 
\begin{eqnarray}
x(t+1) = x_{t+1} = R x_t (1 - x_t), \ \ \ \ \  t=0, 1, 2, \ldots . 
\end{eqnarray}
This is the logistic map as defined in [2].  (In what follows, we will refer to $x_t$ as the population size, with the understanding that it will always be the ratio of the actual population size to the carrying capacity.)
Depending on the value of $R$, the logistic map will generate a population size that is stable, periodic, or chaotic over time.  The behavior of the logistic map can vary a great deal with small changes in $x_0$.  This phenomenon is known as {\it sensitive dependence on initial conditions}, where small changes in the input lead to large changes in the output.

@@

For this project, we used the  model of growth define in INSERT REFERENCE that uses an logicistic growth model on a lattice of organisms coupled with influence from the entire population of organisms.  For each time step $n$, the size of population $i$ at time step $n$ is defined to be
\begin{eqnarray}
x_{i, n+1} = (1 - \epsilon) f_i(x_{i,n}) + \epsilon m_n, \ \ \ (i=1, 2, \ldots N)
\end{eqnarray}
Here $N$ is the number of time steps, $n$ is the current time step (or generation), and $\epsilon$ is the coupling strength of the model to the entire lattice of organisms.   Here the the local growth dynamics of each population $i$ is defined by 
\begin{eqnarray}
f_i(x_{i,n}) = r_i x_{i,n} (1 - {x_{i,n} \over K})
\end{eqnarray}
Here $r_i$ is the reproductive fitness of population $i$ and $K$ is the carrying capacity.

@@

% Figure for part 2
 \begin{figure}[H]
 \centering
    \includegraphics[width=90mm]{prettypicture}

    \caption{ Return map for selected values of  the global coupling strength $\epsilon$:  $\epsilon =0$ (red), $\epsilon = 0.1$ (blue), $\epsilon = 0.25$ (orange), $\epsilon = 0.225$ (aqua), $\epsilon = 0.25$ (dark green), $\epsilon = 3 $ (stars) and $\epsilon = 4$ (black)}
\end{figure}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

>>>>

Define the population size relative to the carrying capacity as  $x_t = n_t / k$ and define $R = birthrate - deathrate$.  Then we  get the following equation for $x_t$: 
\begin{eqnarray}
x(t+1) = x_{t+1} = R x_t (1 - x_t), \ \ \ \ \  t=0, 1, 2, \ldots . 
\end{eqnarray}
This is the logistic map as defined in \cite{Mitchell}  (In what follows, we will refer to $x_t$ as the population size, with the understanding that it will always be the ratio of the actual population size to the carrying capacity.)
Depending on the value of $R$, the logistic map will generate a population size that is stable, periodic, or chaotic over time.  The behavior of the logistic map can vary a great deal with small changes in $x_0$.  This phenomenon is known as {\it sensitive dependence on initial conditions}, where small changes in the input lead to large changes in the output.

@@

% Figure for part 2
% \begin{figure}[H]
 %\begin{subfigure}[b]{0.4\columnwidth}
   % \centering
    %\includegraphics[width=\textwidth]{figure1ab}
     %\caption{ LEFT}
 %   \label{figure1ab}
%\end{subfigure}
%
%\begin{subfigure}[b]{0.4\columnwidth}
 %\includegraphics[width=\textwidth]{figure1cd}
   % \caption{ RIGHT)}
 %\label{figure1cd}
 %\end{subfigure}
 %\caption{A big ole figure}
% \end{figure}

\begin{figure}[H]
\centering
 \includegraphics[width=90mm]{figure1abcd_combined}

   \caption{ SOME CAPTION}
 \label{figure1abcd}
\end{figure}

\subsection{The Walker Model}
For this project, we used the  model of growth define in \cite{Walker}  that uses an logistic growth model on a lattice of organisms coupled with influence from the entire population of organisms.  For each time step $n$, the size of population $i$ at time step $n$ is defined to be
\begin{eqnarray}
x_{i, n+1} = (1 - \epsilon) f_i(x_{i,n}) + \epsilon m_n, \ \ \ (i=1, 2, \ldots N)
\end{eqnarray}
Here $N$ is the number of time steps, $n$ is the current time step (or generation), and $\epsilon$ is the coupling strength of the model to the entire lattice of organisms.   Here the the local growth dynamics of each population $i$ is defined by 
\begin{eqnarray}
f_i(x_{i,n}) = r_i x_{i,n} (1 - {x_{i,n} \over K})
\end{eqnarray}
Here $r_i$ is the reproductive fitness of population $i$ and $K$ is the carrying capacity.

@@

In figure \ref{prettypicture}, we show the return maps for a selection of coupling strengths $\epsilon$.

% Figure for part 2
 \begin{figure}[H]
 \centering
    \includegraphics[width=100mm]{prettypicture}

    \caption{ Return map for selected values of  the global coupling strength $\epsilon$:  $\epsilon =0$ (red), $\epsilon = 0.1$ (blue), $\epsilon = 0.25$ (orange), $\epsilon = 0.225$ (aqua), $\epsilon = 0.25$ (dark green), $\epsilon = 3 $ (stars) and $\epsilon = 4$ (black)}
 \label{prettypicture}
\end{figure}

This return map was using equations LIST EQUATION NUMBERS  in Python using Matplotlib.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
{\bf CHECK THAT BIBITEMS HAVE CORRECT FORMAT }
\begin{thebibliography}{1}

  \bibitem{JIDT}
  JIDT: An information-theoretic toolkit for studying the dynamics of complex systems
Joseph T. Lizier  https://arxiv.org/abs/1408.3270
FIX THIS

\bibitem{Walker} Evolutionary Transitions and Top-Down Causation

\bibitem{Mitchell} ]M. Mitchell, Complexity. Oxford: Oxford University Press, 2011, pp. 27-37.

\bibitem{Flake} G. Flake, The computational beauty of nature. Cambridge, Mass.: The MIT Press, 2011, pp. 139-151.

\bibitem{Walker} Evolutionary Transitions and Top-Down Causation
